Evaluating Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe using radiocarbon data

### 2019-03-24 article/02_Materials_and_Methods.Rmd
reworked Table 1

```{r dprcrosstab, echo=FALSE, tidy=FALSE}
load("../analysis/data/output_data/dprcrosstab.RData")
dprcrosstab %>% 
  unclass() %>% data.frame() %>% 
  knitr::kable(
    caption = "Burial rite distribution in the active dataset.",
    format = "latex",
    booktabs = T,
    escape = F,
    linesep = "\\addlinespace \\hline \\addlinespace",
    align = "l"
  ) %>%
  kableExtra::kable_styling(
    full_width = T, 
    font_size = 9,
    latex_options = "hold_position"
  ) %>%
  kableExtra::add_header_above(c("burial type" = 1, "burial construction" = 3))
```

>>>>

```{r dprcrosstab, echo=FALSE, tidy=FALSE}
load("../analysis/data/output_data/dprcrosstab.RData")
colnames(dprcrosstab)[1:2] <- c("Region", "Burial type")
dprcrosstab %>% 
  dplyr::mutate_at(
    dplyr::vars(tidyselect::one_of("flat", "mound", "unknown")),
    list(~kableExtra::cell_spec(., "latex", bold = . > 100)) 
  ) %>%
  knitr::kable(
    caption = "Burial rite distribution in the active dataset.",
    format = "latex",
    booktabs = T,
    escape = F,
    #linesep = "\\addlinespace \\hline \\addlinespace",
    align = "l"
  ) %>%
  kableExtra::kable_styling(
    full_width = T,
    font_size = 9,
    latex_options = "hold_position"
  ) %>%
  kableExtra::add_header_above(c(" " = 1, " " = 1, "Burial construction" = 3)) %>%
  kableExtra::column_spec(1, width = "2.5cm") %>%
  kableExtra::column_spec(2, width = "1.5 cm") %>%
  kableExtra::column_spec(3:5, width = "0.8cm") %>%
  kableExtra::collapse_rows(1, row_group_label_position = "identity", valign = "top")

```
